MATH 3610 - Project \#1

### 2015-09-27 proj1.tex
Closed form for S

@@

We have now made these differential equations independant:

@@

>>>>

\DeclareMathOperator\erf{erf}

@@

\begin{tikzpicture}[scale=2.0]
	\coordinate[label=below:{$0$}] (origin) at (0,0);
	\draw[<->, thick] (0,2) node (saxis) [above] {$S$}
	|- (3,0) node (taxis) [right] {$t$};

	\coordinate[label=left:{$K$}] (sintercept) at (0,1.5);
	\coordinate[label=below:{$\frac{K}{r_v}$}] (tintercept) at (2.2,0);
	\draw (sintercept) -- (tintercept);
	\fill[gray!20, opacity=0.8] (origin) -- (sintercept) -- (tintercept) -- cycle;

	\draw[dotted] (sintercept) -- (3.0, 1.5);
	\node (valid) at (0.7,0.4) {Valid Region};
	\node (endregion) at (2.3, 1.0) {No-Change Region};
\end{tikzpicture}

In the above figure, once $S(t)$ hits the diagonal line,
	it stays horizontal and keeps its value.

We have now made these differential equations independant,
	within the model's zone of validity:

@@

We present a solution for $S(t)$:

\begin{align}
S(t) & = 
	\frac{e^{ r t (K - \frac{ r_v t}{2})}}
	{\frac{1}{S(0)} + \sqrt{\frac{\pi r}{2 r_v}}
		e^{\frac12 \left( \frac{r}{r_v} \right) K^2}
		\left(\erf\left(  \sqrt{\frac{r}{2 r_v}} (r_v t - K ) \right)
			- \erf\left( - \sqrt{\frac{r}{2 r_v}} K \right) \right)}
\end{align}

From the above expression for the boundary of the valid region,
	we get the following implicit expression for $t_f, S(t_f)$

\begin{align}
S(t_f) = 
	\frac{e^{ r t_f (K - \frac{ r_v t_f }{2})}}
	{\frac{1}{S(0)} + \sqrt{\frac{\pi r}{2 r_v}}
		e^{\frac12 \left( \frac{r}{r_v} \right) K^2}
		\left(\erf\left(  \sqrt{\frac{r}{2 r_v}} (r_v t_f - K ) \right)
			- \erf\left( - \sqrt{\frac{r}{2 r_v}} K \right) \right)}
	& = K - r_v t_f 
\end{align}
